DeepSphere: a graph-based spherical CNN

### 2019-09-18 main.tex
Updates from Overleaf

@@

% !) summary the work of Khasanova
\cite{khasanova2017graphomni} designed a discrete Laplacian that is explicitly intended to work on the sphere with the equiangular sampling. They consider the set $\mathcal G$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes the difference in the response to the polynomial spectral filter $\mathcal F = \mathbf L$ evaluated on images of the same object seen at different latitudes. In other words, they solve the minimization problem
\begin{equation} \label{eq:minimization frossard}
	\min_{W\in\mathcal G} \left|\mathcal{F}\left(\mathbf{y}\left(v_{ e}\right)\right)-\mathcal{F}\left(\mathbf{y}\left(v_{ i}\right)\right)\right|
\end{equation}
for the adjacency matrix $W$, where $\mathbf y(v_i)$ is the image of the object on the sphere centered on the vertex $v_i$, and $\mathcal F (\mathbf y(v_e))$ is the response of the filter at the vertex $v_e$ that lies at the same longitude of the vertex $v_i$ but on the equator. In their work they prove that the optimal weights solving the minimization problem (\ref{eq:minimization frossard}) are given by weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
\begin{equation} \label{eq:frossard weights}
	w_{ij} = \frac{1}{\norm{x_i-x_j}}
\end{equation}

% 2) explain our approach
Our approach is different as we do not miminize eq \ref{eq:minimization frossard}. Instead we inspire ourselves with Belkin, which says that for \emph{uniform sampling} the graph Laplacian converges toward the Laplace-Beltrami. b) The Laplace Beltrami commute with rotation. The following theorem extend the work of Belkin and Nyiogi to fixed sampling \nati{(Including Healpix or not?)}. 
Given a sampling $V = \{x_0, \dots, x_{n-1}\}$ define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing $\sigma_i$. Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.

@@

% 3) Show experimental results
Define the error, show results and comments

>>>>

\cite{khasanova2017graphomni} designed a discrete Laplacian that is explicitly intended to work on the sphere with the equiangular sampling. They consider the set $\mathcal G$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, Sud, West, East) and propose a weighting scheme $w_{ij}$ that minimizes the difference in the response to the polynomial spectral filter $\mathcal F = \mathbf L$ evaluated on images of the same object seen at different latitudes. In other words, they solve the minimization problem
\begin{equation} \label{eq:minimization frossard}
	\min_{W\in\mathcal G} \left|\mathcal{F}\left(\mathbf{y}\left(v_{ e}\right)\right)-\mathcal{F}\left(\mathbf{y}\left(v_{ i}\right)\right)\right|
\end{equation}
for the adjacency matrix $W$, where $\mathbf y(v_i)$ is the image of the object on the sphere centered on the vertex $v_i$, and $\mathcal F (\mathbf y(v_e))$ is the response of the filter at the vertex $v_e$ that lies at the same longitude of the vertex $v_i$ but on the equator. In their work they prove that the optimal weights solving the minimization problem (\ref{eq:minimization frossard}) are given by weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
\begin{equation} \label{eq:frossard weights}
	w_{ij} = \frac{1}{\norm{x_i-x_j}}
\end{equation}

@@

% !) summary the work of Khasanova -> No! to be put in section 2) Method

% 2) explain our approach
We inspire ourselves with Belkin, which says that for \emph{uniform sampling} the graph Laplacian converges toward the Laplace-Beltrami. b) The Laplace Beltrami commute with rotation. The following theorem extend the work of Belkin and Nyiogi to fixed sampling \nati{(Including Healpix or not?)}. 
Given a sampling $V = \{x_0, \dots, x_{n-1}\}$ define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing $\sigma_i$. Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.

@@

% 3) Show experimental results
Define the error, show results and comments
\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{figure_architecture_v3}
	\caption{Example architecture from \cite{perraudin2019deepsphere}.
		Global tasks need a spatial summarization: the FCN variant is rotation invariant (and accepts inputs of varying sizes), while the CNN variant is not.
		Dense tasks (when the output lives on the sphere, like segmentation) are rotation equivariant.
	}
	\label{fig:architecture}
\end{figure}
